%-------------------------
% Resume in Latex
% Author : Sanjay K V
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% only for pdflatex
% \input{glyphtounicode}

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underilne
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}


% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 
%% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - serif
% \titleformat{\section}{
%   \vspace{2pt} \scshape \raggedright\large % header section
% }{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]

% TODO EBSERIES
% sans serif sections
\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large % header section
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

% only for pdflatex
% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ % top row of resume entry
      \text{#3} & {\color{dark-grey} \small #4}\\ % second row of resume entry
    \end{tabular*}\vspace{-4pt}
} 

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% CHANGED default leftmargin  0.15 in
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Large SANJAY KANAKKOT VISWANATHAN} \\ \vspace{4pt}
    \small \faPhone* \texttt{+61 448716345} \hspace{1pt} $|$
    \hspace{1pt} \faEnvelope \hspace{2pt} \texttt{sanjay.kanakkot@gmail.com} \hspace{1pt} $|$ 
    \hspace{1pt} \faLinkedin \hspace{2pt} \texttt{\href{https://www.linkedin.com/in/sanjay-k-v/}{\myuline {sanjay-k-v}}} \hspace{1pt} $|$
    \hspace{1pt} \faGithubSquare \hspace{2pt}\texttt{{\href{https://github.com/sanjay-kv}{\myuline {sanjay-kv}}}}
    \hspace{1pt} \faInfoCircle \hspace{2pt}\texttt{{\href{http://sanjaykv.com}{\myuline {sanjaykv.com}}}}
     
\end{center}

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Truuth}{Feb. 2023 -- July. 2023}
      {Data Scientist Intern }{Sydney, Australia}
      \resumeItemListStart
        \resumeItem{Using Azure to design, build, and improve text format check in the organization and quantify accuracy.}
        \resumeItem{Implemented Adaptive Image Enhancement models and improved Visual feature check by \textbf{90 percent.}}
      \resumeItemListEnd


    \resumeSubheading
      {Recode Hive}{May. 2021 -- Jan. 2023}
      {Founder/ Head of Content (\href{https://recodehive.com}{\myuline {recodehive.com}})}{Kochi, India}
      \resumeItemListStart
        \resumeItem{Launched ebook and courses. Scaled social media presence to \textbf{13k Followers in 6 months.}}
        \resumeItem{\textbf{Delivered 50+ talks} on ML, Data Science, Open source contributions and taught 2000+ students, Cloud Advocate. }
        \resumeItem{\textbf{Highlights}:
            Guest speaker for\href{https://adaptconvention.com/speakers/}{\myuline { Adapt Convention (2020,21)}}, GDG Germany, Girlscript- Rourkela, Google CS events.
            }
      \resumeItemListEnd

    \resumeSubheading
      {Larsen and Toubro Infotech Ltd. - LTI}{Aug. 2018 -- May. 2021}
      {Software Engineer}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Worked with Cross-functional projects, developed interactive dashboards and reports in SAP C4C for clients.}
        \resumeItem{Worked closely with stakeholders on Power BI \textbf{Data modeling with SAP raw data} with team of 4.}
        \resumeItem{ Completed 5 Projects. Created inventory tool which improved team productivity by\textbf{ 20 percentage}.}

    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------

\section{PROJECTS}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Stack Overflow survey data Analysis}} {Sept. 2019 -- Mar. 2021}
          \resumeItemListStart
            \resumeItem{Analysed Stack Overflow \textbf{survey data set of 3 years}, and found highest paid job, programming languages, etc.}
            \resumeItem{Accomplished predicting what caused job satisfaction, Growth of language using Machine Learning. 
            \href{https://github.com/sanjay-kv/Stackoverflow-Analysis}{\myuline {GitHub Link}}}
          \resumeItemListEnd
  
    \resumeSubHeadingListEnd
    
%-----------PROGRAMMING SKILLS-----------
\section{SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Programming/language:} { Python, Git, HTML, CSS, MySQL, SQL}\vspace{2pt} \\
     \textbf{Tools/ Frameworks:} { Numpy, Pandas, Sklearn, PowerBI, Google Analytics, Azure, Excel, Visual Studio Code.} \\
     \textbf{Hobbies/ Other skills:} { Presentations, Product Launch, Product Management, Product Strategies, Sales and Marketing}\
     
    }}
 \end{itemize}


%-------------------------------------------    
%-----------VOLUNTEER EXPERIENCE-----------
\section{VOLUNTEER EXPERIENCE}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{GitHub Campus Expert:} {Completed 6 Weeks of \href{https://githubcampus.expert/sanjay-kv/}
{\myuline {training}} from GitHub Team and hosted 10 workshops so far.}\vspace{2pt} \\
     \textbf{Google Crowdsource Influencer:} {Received \href{https://crowdsource.google.com/about/blog/community-spotlight-friendship/}
{\myuline {recognition}} award for \textbf{mentoring} and build local communities.}\\
          \textbf{Google Local guide:} Added 200+ km using Road mapper, Featured and invited to California office for proactive work.}}
  
 \end{itemize}


%-------------------------------------------    

%-----------EDUCATION-----------
\section {EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Macquarie University}{Feb. 2021 -- June. 2023}
      {Master of Data Science}{North Ryde, NSW, Australia}
      	\resumeItemListStart
    	\resumeItem {\textbf{Coursework}: Database, Machine Learning, Big Data}
  \resumeItem {\textbf{Achievements}: Helped GitHub to  launch \href{https://education.github.com/globalcampus/exchange/}
{\myuline {GitHub community exchange program}}}\\
\textbf{Google Explore ML Facilitator}, Worked with Product Team, \href{https://rsvp.withgoogle.com/events/explore-ml-with-crowdsource-workshops-on-air/facilitators}
{\myuline {Hosted 10 workshops.}}}
        \resumeItemListEnd

  
  \resumeSubHeadingListStart
    \resumeSubheading
      {SRM Institute of Science and Technology}{June. 2014 -- May. 2018}
      {Bachelor in Technology(B.Tech) - Computer Science - CGPA 7.8/10}{Chennai, India}

  \resumeSubHeadingListEnd

%


%-----------PROGRAMMING SKILLS-----------
\section{CERTIFICATIONS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
           \resumeItemListStart
            \resumeItem{Google Analytics certification Beginner and intermediate, Google Data Studio certification.}
         \resumeItem{LinkedIn Learning certification on \textbf{diversity, inclusion, and belonging}. }
          \resumeItemListEnd    
    }}
 \end{itemize}


%-------------------------------------------

%-----------EDUCATION-----------
\section {REFERENCES}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Mike Simpson }{Worked during Aug. 2023 -- Feb, June}
      {CEO, Co-founder at Truuth}{Sydney, Australia}
      	\resumeItemListStart
    	\resumeItem {\textbf{Email}: Mike.simpson@truuth.id}
      	\resumeItem {\textbf{Mob No}: +61 0432545256}
  \\
  
        \resumeItemListEnd
  \resumeSubHeadingListStart
    \resumeSubheading
      {Pulkit Jain (Ex-colleague)}{Worked during Aug. 2018 -- May. 2021}
      {Senior Business Analyst at Uber}{Bangalore, India}
      	\resumeItemListStart
    	\resumeItem {\textbf{Email}: pulkitj@uber.com}
      	\resumeItem {\textbf{Mob No}: +91 9940628145}
  
        \resumeItemListEnd

  
  \resumeSubHeadingListStart
    \resumeSubheading
      {Iswarya Balakrishnan}{April. 2020 -- Sept. 2021}
      {Strategic Partner Development Manager, Google}{Bangalore, India}
	\resumeItemListStart
    	\resumeItem {\textbf{Email}: ibalakrishnan@google.com}
      	\resumeItem {\textbf{Mob No}: +91 6366256630}
  
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%
\end{document}
%-----------PROGRAMMING SKILLS-----------



